%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{\textbf{\Large Senior Security Engineer}} % Job title
{GFG eCommerce Technologies GmbH} % Organization
{\textbf{\Large Berlin, Germany}} % Location
{Nov. 2019 - Present} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {\textbf{\large DevSecOps oriented role.}}
\item {\textbf{\large Developing testing scripts and procedures.}}
\item {\textbf{\large Bug bounty - h1 based, reports validations, response, and closure.}}
\item {\textbf{\large Performing infrastructure and application security assessments.}}
\item {\textbf{\large Developing and leveraging custom exploits.}}
\item {\textbf{\large Developing processes, implementing tools and techniques to perform ongoing security assessments of the environment.}}
\item {\textbf{\large Working on improving provided security services, including the continuous enhancement of existing methodology material.}}
\item {\textbf{\large Conducting security pieces of training across different teams for secure coding practices, DevSecOps, and cybersecurity awareness.}}
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{\textbf{\Large Lead Security Engineer}} % Job title
{Paytm, One97 Communications Limited} % Organization
{\textbf{\Large Noida, India}} % Location
{Aug. 2016 - Sept. 2019} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {\textbf{\large Security Architecture Review of applications and hosted infrastructure.}}
\item {\textbf{\large Bug bounty - Reports validation, response, and closure.}}
\item {\textbf{\large Application security testing (Web, Android, iOS and API endpoints).}}
\item {\textbf{\large Static and source code analysis (SAST and DAST).}}
\item {\textbf{\large Infrastructure vulnerability assessments and penetration testing.}}
\item {\textbf{\large Carried out red teaming activities.}}
\item {\textbf{\large Implemented Akamai WAF, Siteshield and other services on critical end-points (Started this project from scratch).}}
\item {\textbf{\large SecDevOps and end to end product security.}}
\item {\textbf{\large Conducted security pieces of training across different teams. Content included Secure coding practices, DevOps Security and cybersecurity awareness.}}
\item {\textbf{\large Security audits across different verticals.}}
\item {\textbf{\large Incident response and handling.}}
\item {\textbf{\large Ensured PCI-DSS, RBI PPS, NPCI and RBI compliances.}}
\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Security Engineer} % Job title
    {Freshworks Inc. (formerly Freshdesk)} % Organization
    {Chennai, India} % Location
    {Feb. 2015 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web Applications and API penetration testing.}
        \item {Bug bounty program - validations and response.}
        \item {Ensured the security best practices and compliance.}
        \item {Infused security in SDLC and ensured the security sign-off to weekly releases.}
        \item {Security reviews for AWS based cloud infrastructure on the timely basis.}
        \item {Vulnerability Assessment (VA) and Penetration Testing (PT) of cross-platform apps and infra.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Security Trainer} % Job title
    {NT Global} % Organization
    {East Africa} % Location
    {July 2014 – Jan 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained Government Organization people over penetration testing and ethical hacking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
