% experience.tex

\section{Professional Experience}

% ---Experience 1---
\subsection{Group Head of Product Security \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Nov 2019 -- Present}
\subsubsection{Expedia Group, Inc. \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Wexford, Ireland} \vspace{0.15cm}

\begin{itemize}
    \item[\textrightarrow] \textit Established a global product security strategy, reducing critical vulnerabilities by 60\% across all platforms. \vspace{0.1cm}
    \item[\textrightarrow] \textit Led the implementation of a secure dev lifecycle, improving time-to-fix by 45\%. \vspace{0.1cm}
    \item[\textrightarrow] \textit Directed a team of 5 engineers to achieve 100\% PCI-DSS compliance. \vspace{0.1cm}
    \item[\textrightarrow] \textit Integrated advanced threat modeling processes, which preventied 70+ high risk vulnerabilities pre-deployment. \vspace{0.1cm}
    \item[\textrightarrow] \textit Launched a centralized incident response program, reducing mean time to resolve (MTTR) by 40\%. \vspace{0.1cm}
    \item[\textrightarrow] \textit Collaborated with product teams to implement security-by-design principles to increase customer trust. \vspace{0.1cm}
    \item[\textrightarrow] \textit Deployed a continuous monitoring system for application security, detecting and mitigating 200+ threats annually.
\end{itemize}

% ---Experience 2---
\subsection{Application Security Engineer \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Aug 2016 -- Sep 2019}
\subsubsection{PayPal S.à r.l. \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Paris, France} \vspace{0.15cm}

\begin{itemize}
	\item[\textrightarrow] \textit Reduced API vulnerabilities by 45\% via implementation of automated API security testing tools. \vspace{0.1cm}
	\item[\textrightarrow] \textit Designed a secure authentication framework, that has decreased the incidents of account compromise by 30\%. \vspace{0.1cm}
	\item[\textrightarrow] \textit Conducted regular red team exercises, uncovering and mitigating 150+ critical security gaps. \vspace{0.1cm}
	\item[\textrightarrow] \textit Integrated static and dynamic code analysis into CI/CD pipelines, for reducing the vulnerabilities detection time by 50\%. \vspace{0.1cm}
	\item[\textrightarrow] \textit Collaborated with global teams to implement secure payment protocols, enhancing fraud prevention by 20\%. \vspace{0.1cm}
	\item[\textrightarrow] \textit Implemented a secure SDLC process, that decreased the average time to resolve vulnerabilities by 40\%. \vspace{0.1cm}
	\item[\textrightarrow] \textit Collaborated with development teams to fix 100+ critical security issues.
\end{itemize}

% ---Experience 3---
\subsection{Senior Security Engineer \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Feb 2015 -- Aug 2016}
\subsubsection{Doctolib  \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Paris, France}

\begin{itemize}
    \item All details are at my \bluelink{https://www.linkedin.com/in/kevin-mitnick-697a53207}{LinkedIn Profile}.
\end{itemize}	

% ---Experience 4---
\subsection{Security Engineer \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Jul 2014 -- Nov 2014}
\subsubsection{Deezer  \texorpdfstring{\hspace*{\fill}}{\hspace*{\fill}} \normalfont Nantes, France}

\begin{itemize}
    \item All details are at my \bluelink{https://www.linkedin.com/in/kevin-mitnick-697a53207}{LinkedIn Profile}.
\end{itemize}
